---
title: "WordCloud2"
author: "Sarah Widgodsky & Nathan Cooper"
date: "October 19, 2017"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

```

```{r libraries, eval=TRUE}
suppressMessages(suppressWarnings(library("tm")))
suppressMessages(suppressWarnings(library("wordcloud")))
suppressMessages(suppressWarnings(library("tidyr")))
suppressMessages(suppressWarnings(library("stringr")))
suppressMessages(suppressWarnings(library("SnowballC")))
```

I start with Sarah's code for putting the data into data frames:
```{r data_input, eval=TRUE}
joblistny <- read.csv("https://raw.githubusercontent.com/delagroove/dataScience/master/jobOffers_ny.csv", stringsAsFactors=FALSE)
joblistma <- read.csv("https://raw.githubusercontent.com/delagroove/dataScience/master/jobOffers_final_with_dupes_reduced.csv", stringsAsFactors = FALSE)
joblistsf <- read.csv("https://raw.githubusercontent.com/delagroove/dataScience/master/jobOffers_SF.csv", stringsAsFactors=FALSE)
joblistsf <- joblistsf[,-1]

joblisttidy <- rbind(joblistma, joblistny, joblistsf)
joblisttidy <- joblisttidy[,-5]
joblisttidy <- subset(joblisttidy, duplicated(joblisttidy)==FALSE)
joblisttidy$location <- unlist(str_extract_all(joblisttidy$location, "[[:upper:]]{1}[[:lower:]]{2,}, [[:alpha:]]{2}|[[:upper:]]{1}[[:lower:]]{2,} [[:alpha:]]{2,}, [[:alpha:]]{2}"))
head(joblisttidy)
```

Now I will be using the description column to create a word cloud.
https://www.r-bloggers.com/building-wordclouds-in-r/
https://georeferenced.wordpress.com/2013/01/15/rwordcloud/
Were my sources for the procedure

```{r cloud, eval=TRUE}
dsCloud <- Corpus(VectorSource(joblisttidy$description))
dsCloud <- tm_map(dsCloud, removePunctuation)
dsCloud <- tm_map(dsCloud, tolower)
dsCloud <- tm_map(dsCloud, removeWords, c("data","science","scientist" , "you" ,"will",stopwords('english')))
wordcloud(dsCloud, max.words = 50, random.order = FALSE, scale=c(3,.15),random.color = FALSE,colors=palette())
```

I had to remove a few words like: Data, Science, Scientist, you, and will along with the stop words (e.g., "the"). Note that text stemming was not useful in this application as it truncated words like experience and business. 